Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/mdl.tex
Explain domains

\subsection{Domains}
Potter's Wheel presents an algorithm for deriving a common structure for a set of strings by breaking each string down into a sequence of domains. These domains are described by an interface that includes:
\begin{itemize}
\item A required inclusion function to test for membership in the domain (\texttt{match})
\item An optional function to compute the number of values in the domain with a given length (\texttt{cardinality})
\item An optional function to update statistics for the domain based on a given value (\texttt{updateStatistics})
\item An optional function to prevent consideration of a domain that is redundant (\texttt{isRedundantAfter}).
\end{itemize}

In our approach, we implement all of these functions, but with significant changes to the last one, which we will describe below.

>>>>

\subsection{Domains}
Potter's Wheel presents an algorithm for deriving a common structure for a set of strings by breaking each string down into a sequence of \textit{domains}. A domain is a set of strings, with a few optional statistical properties. They are defined by an interface that includes:
\begin{itemize}
\item A required inclusion function to test for membership in the domain (\functionname{match}). 
For example, the domain \functionname{<Digits>} would return true for the string \functionname{"123"} 
and false for the string \functionname{"abc"}.
\item An optional function to compute the number of values in the domain with a given length (\functionname{cardinality}).
For example, the domain for three letter month names (\functionname{MMM}) would return $12$ for the length $3$ and $0$ otherwise.
\item An optional function to update statistics for the domain based on a given value (\functionname{updateStatistics}).
For example, the domain \functionname{MMM} might keep a histogram of how frequently each month was encountered.
\item An optional function to prevent consideration of a domain that is redundant (\functionname{isRedundantAfter}).
For example, the domain \functionname{<Digits>} would be redundant after itself 
(\ie there is no difference between a single run of digits and two adjacent runs.)
\end{itemize}

In our approach, we implement all of these functions, but with significant changes to the last one to increase level of pruning applied during
domain enumeration. These changes will be described below.
